---
title: "Shaofei Shen_45503745_assignment 3_Q2"
author: "Shaofei Shen"
date: "2019/10/3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Q2
#### profit testing process
##### create the meltiple decrement table
Input the data from table
```{r}
x_2<-c()
x_2<-c(30:39)
qd<-c()
qd[30:39]<-c(0.00043,.00042,.00041,.00040,.00041,.00042,.00043,.00045,.00049,.00053)
qw<-c()
qw[30:39]<-c(0.25,0.2,0.175,0.150,0.150,0.150,0.150,0.150,0.150,1)
```
 
The dependent rates is given by 
$(aq)_x^d=q_x^d(1-0.5q_x^w)$,$(aq)_x^w=q_x^w(1-0.5q_x^d)$,$(ad)_x^d=(al)_x*(aq)_x^d$
```{r}
aqx.d<-c()
aqx.d[30:39]<-qd[30:39]*(1-0.5*qw[30:39])
aqx.w<-c()
aqx.w[30:39]<-qw[30:39]*(1-0.5*qd[30:39])
```

initialise $(ad)_x^d$ and $(ad)_x^w$ and the formula is given by $(ad)_x^d=(al)_x*(aq)_x^d$,$(ad)_x^w=(al)_x*(aq)_x^w$, $(al)_{x+1}=(al)_x-(ad)_x^d-(ad)_x^w$
create the melti-decrement table.
```{r}
al.x<-c()
ad.x.d<-c()
ad.x.w<-c()
al.x[30]<-100000
for (j in 30:40) {
  ad.x.d[j]<-al.x[j]*aqx.d[j]
  ad.x.w[j]<-al.x[j]*aqx.w[j]
  al.x[j+1]<-al.x[j]-ad.x.d[j]-ad.x.w[j]
}
MDtable <- cbind(x_2[30:40],qd[30:40],qw[30:40],aqx.d[30:40],aqx.w[30:40],al.x[30:40],ad.x.d[30:40],ad.x.w[30:40])
colnames(MDtable) <- c("x","qd", "qw","(aq)d","(aq)w","(al)","(ad)d", "(ad)w")
MDtable
```
##### create the unit fund table 
The vector of premium $P_t$ is
```{r}
prems<-c()
prems[30:39]<-c(rep(5000,10))
prems[30:39]
```
The Premium-based fee is $P_t*(1-a_t)=5000*45\%$ in year 1 and $5000*1\%$ thereafter.
```{r}
pbf<-c()
pbf[30:39]<-c(prems[30]*0.45,prems[31:39]*0.01)
pbf[30:39]
```
The Buy/Sell margin is $b*P_t *a_t=0.5\%*P_t*(1-45\%)$ in year 1, $0.5\%*P_t*(1-1\%)$ thereafter.
```{r}
bsm<-c()
bsm[30:39]<-c(0.005*prems[30]*(1-0.45),0.005*prems[31:39]*(1-0.01))
bsm[30:39]
```
The Invested premium $IP_t=P_t - Premiumbased\,fee - Buy/Sell\,margin$
```{r}
IP<-c()
IP[30:39]<-prems[30:39]-pbf[30:39]-bsm[30:39]
IP[30:39]
```
Value of unit at the end of the year
$VU_0=IP_0(1+i)(1-m)\;for\;t=0$;$VU_t=(VU_{t-1}+IP_t)(1+i)(1-m)\;for\;t=1,2,3,...$ 
with unit fund earning rate on the unit fund is $i=10\%$, the asset fee is $m=0.3\%$
```{r}
i<-0.1;m<-0.003
VU<-c()
for (j in 30:39) {
  VU[30]<-IP[30]*(1+i)*(1-m)
  VU[j]<-(VU[j-1]+IP[j])*(1+i)*(1-m)
}
VU[30:39]
```
we need to compute the expected cashflow for unit fund
expected investment premium 
$Expected\,Invested\,Premium(EIP_t)=IP_t\frac{(al)_{29+t}}{(al)_{30}}$
```{r}
EIP.u<-c()
EIP.u[30:39]<-IP[30:39]*al.x[30:39]/al.x[30]
EIP.u[30:39]
```
expected value of units 
$Expected\,Value\,of\,Units(EVU_t)=VU_t\frac{(al)_{30+t}}{(al)_{30}}$
```{r}
EVU.u<-c()
EVU.u[30:39]<-VU[30:39]*al.x[31:40]/al.x[30]
EVU.u[30:39]
```
expected interest
$i*(EVU_{t-1}+EIP_t)$
```{r}
int.u<-c()
int.u[30:39]<-c(i*EIP.u[30],i*(EVU.u[30:38]+EIP.u[31:39]))
int.u[30:39]
```
tranfer for non-unit fund is calculated by 
$EIP_1+Interst_1-EVU_1$ in Year 1 and $EVU_{t-1}+EIP_t+Interst_t-EVU_t$ in following years.
```{r}
Tmsfr.u<-c()
for (j in 30:39) {
  Tmsfr.u[30]<-EIP.u[30]+int.u[30]-EVU.u[30]
  Tmsfr.u[j]<-EVU.u[j-1]+EIP.u[j]+int.u[j]-EVU.u[j]
}
Tmsfr.u[30:39]
```
create the unit fund table 
```{r}
t<-c(1:10)
UFtable <- cbind(t,IP[30:39],VU[30:39],EIP.u[30:39],int.u[30:39],EVU.u[30:39],Tmsfr.u[30:39])
colnames(UFtable) <- c("year","invested premium","value of units", "expected invested premium","expected interest","expected value of units","transfer")
UFtable
```
#### create the non-unit fund table 
withour probility 
calculate expense 
```{r}
exp<-c()
exp[30:39]<-c(prems[30]*0.45+58,58*1.2^(t[2:10]-1))
exp[30:39]
```

Death and Surrender Benefit are equal to the sell value of units.
```{r}
dsbft<-c()
dsbft[30:39]<-VU[30:39]
dsbft[30:39]
```

Expected cashflows 
Expected premium-based fee for the Non-unit Fund
$Expected\,premium\,based\,fees=premium\,based\,fees\,\frac{(al)_{29+t}}{(al)_{30}}$
```{r}
Epbf.nu<-c()
Epbf.nu[30:39]<-pbf[30:39]*al.x[30:39]/al.x[30]
Epbf.nu[30:39]
```
expected buy/sell margin 
$Expected\,Buy\,Sell\,margins=Buy\,Sell\,margins\,\frac{(al)_{29+t}}{(al)_{30}}$
```{r}
Ebsm.nu<-c()
Ebsm.nu[30:39]<-bsm[30:39]*al.x[30:39]/al.x[30]
Ebsm.nu[30:39]
```
Expected expense 
$Expected\,Expenses=Expenses\,\frac{(al)_{29+t}}{(al)_{30}}$
```{r}
Eexp.nu<-c()
Eexp.nu[30:39]<-exp[30:39]*al.x[30:39]/al.x[30]
Eexp.nu[30:39]
```
Expected death benefit for non-unit fund 
$Expected\,Death\,Benefits=Death\,Benefits\,\frac{(ad)_{29+t}^d}{(al)_{30}}$
```{r}
Edbft.nu<-c()
Edbft.nu[30:39]<-dsbft[30:39]*ad.x.d[30:39]/al.x[30]
Edbft.nu[30:39]
```

Expected surrender benefit 
$Expected\,Surrender\,Benefits=Surrender\,Benefits\,\frac{(ad)_{29+t}^w}{(al)_{30}}$
```{r}
Esbft.nu<-c()
Esbft.nu[30:39]<-dsbft[30:39]*ad.x.w[30:39]/al.x[30]
Esbft.nu[30:39]
```

The Non-unit fund earning rate is 8%.$Expected\,interest=i*(Expected\,premium\,based\,fees+Expected\,Buy\,Sell\,margins-Expected\,Expenses)$
```{r}
i.nu<-0.08
int.nu<-c()
int.nu[30:39]<-i.nu*(Epbf.nu[30:39]+Ebsm.nu[30:39]-Eexp.nu[30:39])
int.nu[30:39]
```

#### (a)
The transfers are calculated by 
$Expected\,premium\,based\,fees+Expected\,Buy\,Sell\,margins-Expected\,Expenses+Expected\,Interest+Expected\,transfer\,from\,Unit\,Fund-Expected\,death\,benefits-Expected\,surrender\,benefits$
It gives the profit signiture
```{r}
Tmsfr.nu<-c()
Tmsfr.nu[30:39]<-Epbf.nu[30:39]+Ebsm.nu[30:39]-Eexp.nu[30:39]+int.nu[30:39]+Tmsfr.u[30:39]-Edbft.nu[30:39]-Esbft.nu[30:39]
Tmsfr.nu[30:39]
```
create the non-unit fund table 
without probability 
```{r}
nUFtable_1 <- cbind(t,pbf[30:39],bsm[30:39],exp[30:39],dsbft[30:39])
colnames(nUFtable_1) <- c("year","premium based fee","buy sell margin", "expense","death/sur benefit")
nUFtable_1
```
create the expected cashflow table 
```{r}
nUFtable_2 <- cbind(t,Epbf.nu[30:39],Ebsm.nu[30:39],Eexp.nu[30:39],int.nu[30:39],Tmsfr.u[30:39],Edbft.nu[30:39],Esbft.nu[30:39],Tmsfr.nu[30:39])
colnames(nUFtable_2) <- c("year","expected premium based fee","expected buy sell margin", "expected expense","expected interest","Trnsfr ufund", "death bft", "surr bft", "transfer")
nUFtable_2
```
The expected present value of non-unit fund transfer at 12.5% is 
$EPV=\sum_{t=1}^{10}(1+12.5\%)^{-t}\,Transfer_t$
```{r}
EPV.Tmsfr.nu<-sum(1.125^(-t)*Tmsfr.nu[30:39])
EPV.Tmsfr.nu
```
So the expected present value of transfer is  34.67393

The profit measure is $\frac{PV\,of\,transfers\,at\,12.5\%}{First\,year\,premium}$
```{r}
prob<-EPV.Tmsfr.nu/prems[30]
prob
```

#### (b)
##### Method 1
Using knitr package and purl, we can convert our R markdown in to R script. Delete all the outputs and put it into a function. Set the transfer in Year 10 as output and  Value of unit in Year 9 as input. since we need to change the policy value to zeroise and make the negative transfer(year 10) to zero.
```{r}
func<-function(s){
x_2<-c()
x_2<-c(30:39)
qd<-c()
qd[30:39]<-c(0.00043,.00042,.00041,.00040,.00041,.00042,.00043,.00045,.00049,.00053)
qw<-c()
qw[30:39]<-c(0.25,0.2,0.175,0.150,0.150,0.150,0.150,0.150,0.150,1)


## ------------------------------------------------------------------------
aqx.d<-c()
aqx.d[30:39]<-qd[30:39]*(1-0.5*qw[30:39])
aqx.w<-c()
aqx.w[30:39]<-qw[30:39]*(1-0.5*qd[30:39])


## ------------------------------------------------------------------------
al.x<-c()
ad.x.d<-c()
ad.x.w<-c()
al.x[30]<-100000
for (j in 30:40) {
  ad.x.d[j]<-al.x[j]*aqx.d[j]
  ad.x.w[j]<-al.x[j]*aqx.w[j]
  al.x[j+1]<-al.x[j]-ad.x.d[j]-ad.x.w[j]
}



## ------------------------------------------------------------------------
prems<-c()
prems[30:39]<-c(rep(5000,10))



## ------------------------------------------------------------------------
pbf<-c()
pbf[30:39]<-c(prems[30]*0.45,prems[31:39]*0.01)
pbf[30:39]


## ------------------------------------------------------------------------
bsm<-c()
bsm[30:39]<-c(0.005*prems[30]*(1-0.45),0.005*prems[31:39]*(1-0.01))
bsm[30:39]


## ------------------------------------------------------------------------
IP<-c()
IP[30:39]<-prems[30:39]-pbf[30:39]-bsm[30:39]
IP[30:39]


## ------------------------------------------------------------------------
i<-0.1;m<-0.003
VU<-c()
for (j in 30:39) {
  VU[30]<-IP[30]*(1+i)*(1-m)
  VU[j]<-(VU[j-1]+IP[j])*(1+i)*(1-m)
}
VU[38]<-s


## ------------------------------------------------------------------------
EIP.u<-c()
EIP.u[30:39]<-IP[30:39]*al.x[30:39]/al.x[30]



## ------------------------------------------------------------------------
EVU.u<-c()
EVU.u[30:39]<-VU[30:39]*al.x[31:40]/al.x[30]
EVU.u[30:39]


## ------------------------------------------------------------------------
int.u<-c()
int.u[30:39]<-c(i*EIP.u[30],i*(EVU.u[30:38]+EIP.u[31:39]))



## ------------------------------------------------------------------------
Tmsfr.u<-c()
for (j in 30:39) {
  Tmsfr.u[30]<-EIP.u[30]+int.u[30]-EVU.u[30]
  Tmsfr.u[j]<-EVU.u[j-1]+EIP.u[j]+int.u[j]-EVU.u[j]
}



## ------------------------------------------------------------------------
t<-c(1:10)


## ------------------------------------------------------------------------
exp<-c()
exp[30:39]<-c(prems[30]*0.45+58,58*1.2^(t[2:10]-1))



## ------------------------------------------------------------------------
dsbft<-c()
dsbft[30:39]<-VU[30:39]



## ------------------------------------------------------------------------
Epbf.nu<-c()
Epbf.nu[30:39]<-pbf[30:39]*al.x[30:39]/al.x[30]



## ------------------------------------------------------------------------
Ebsm.nu<-c()
Ebsm.nu[30:39]<-bsm[30:39]*al.x[30:39]/al.x[30]



## ------------------------------------------------------------------------
Eexp.nu<-c()
Eexp.nu[30:39]<-exp[30:39]*al.x[30:39]/al.x[30]



## ------------------------------------------------------------------------
Edbft.nu<-c()
Edbft.nu[30:39]<-dsbft[30:39]*ad.x.d[30:39]/al.x[30]



## ------------------------------------------------------------------------
Esbft.nu<-c()
Esbft.nu[30:39]<-dsbft[30:39]*ad.x.w[30:39]/al.x[30]



## ------------------------------------------------------------------------
i.nu<-0.08
int.nu<-c()
int.nu[30:39]<-i.nu*(Epbf.nu[30:39]+Ebsm.nu[30:39]-Eexp.nu[30:39])


## ------------------------------------------------------------------------
Tmsfr.nu<-c()
Tmsfr.nu[30:39]<-Epbf.nu[30:39]+Ebsm.nu[30:39]-Eexp.nu[30:39]+int.nu[30:39]+Tmsfr.u[30:39]-Edbft.nu[30:39]-Esbft.nu[30:39]





## ------------------------------------------------------------------------
EPV.Tmsfr.nu<-sum(1.125^(-t)*Tmsfr.nu[30:39])



## ------------------------------------------------------------------------
prob<-EPV.Tmsfr.nu/prems[30]

Tmsfr.nu[39]
}
uniroot(func,c(60000,70000))
```
The new policy value in year 9 is 67319.02 and we can double check if the transfer at Year 10 is 0.
```{r}
func(67319.02)
```
We can see that the transfer in last year is almost zero. The difference might due to rounding error.

###### Method 2
The separate policy value is 
```{r}
policy_value<-c()
policy_value[30:39]<-VU[30:39]
policy_value[30:39]
```
We now try to find the changed policy value in year 9 to make the vaule of transfer in the final year is zero.
```{r}
f<-function(p)
  (abs(Epbf.nu[39]+Ebsm.nu[39]-Eexp.nu[39]+int.nu[39]-Edbft.nu[39]-Esbft.nu[39]+(EIP.u[39]+(EIP.u[39]+p*al.x[39]/al.x[30])*i+p*al.x[39]/al.x[30])))
nlm(f,VU[38])
```
#### (c)
The  new policy value in year 9 should be changed to 67319.02.
```{r}
policy_value[38]<-67319.02
policy_value[30:39]
```
New Expected policy value
```{r}
Epolicy_value<-c()
Epolicy_value[30:39]<-policy_value[30:39]*al.x[31:40]/al.x[30]
Epolicy_value[30:39]
```
Generate the new tranfer to non-unit fund vector 
```{r}
Tmsfr.nu.c<-c()
for (j in 30:39) {
  Tmsfr.nu.c[30]<-EIP.u[30]+int.u[30]-Epolicy_value[30]
  Tmsfr.nu.c[j]<-Epolicy_value[j-1]+EIP.u[j]+int.u[j]-Epolicy_value[j]
}
Tmsfr.nu.c[30:39]
```
generate the new profit signature
```{r}
profit.sig<-c()
profit.sig[30:39]<-Epbf.nu[30:39]+Ebsm.nu[30:39]-Eexp.nu[30:39]+int.nu[30:39]+Tmsfr.nu.c[30:39]-Edbft.nu[30:39]-Esbft.nu[30:39]
profit.sig[30:39]
```
The last negative transfer is due to the approximation problem, which can be rounded to zero.
The expected present value of the changed transfer at 12.5% is 
```{r}
EPV.Transfer.c<-c()
EPV.Transfer.c<-sum(1.125^(-t)*profit.sig[30:39])
EPV.Transfer.c
```
NPV decreased (before zeroise:34.67393 ;after zeroise: 34.64735). As the negative transfer occures in time 10, we have premmaturely release surplus in the earlier year. We adjust the cashflow at time 9 to make the transfer is 0 instead of negative. Money has been held back in the Unit Fund at time 9 (rather than being released to shareholders) to give a zero transfer at time 10. Since these additional funds earn only 10% p.a. interest in the Unit Fund, whereas the discount rate is 12.50%, overall the business is now (slightly) less profitable.